Reproducing Project 3
------------------------
**By: Mitali Sathaye and Saqib Ali**


Load Packages
------
```{r}
source("../.rProfile", echo = FALSE)
```

These are the four databases that we are going to work with for our project.

```{r}
source("../01 Data/DataSubsets.R", echo = TRUE)
```




**INNER JOIN**
Here we joined each of the four tables and wanted to see how much each sector (Urban vs Rural Vs National) from each country spent on only Jewelry
```{r}
source("../02 Data Wrangling/InnerJoin.R", echo = TRUE)
```
*Plot*
```{r}
source("../03 Visualizations/InnerJoinPlot.R", echo = TRUE)
```


**FULL JOIN**
Here we are showing only the countries where the urban population spends more on both poultry and rice
```{r}
source("../02 Data Wrangling/FullJoin.R", echo = TRUE)
```
*Plot*
```{r}
source("../03 Visualizations/FullJoinPlot.R", echo = TRUE)
```

**LEFT JOIN**
Here we are showing only the countries where the urban population spends more on tobacco but not necessarily on jewelry
```{r}
source("../02 Data Wrangling/LeftJoin.R", echo = TRUE)
```
*Plot*
```{r}
source("../03 Visualizations/LeftJoinPlot.R", echo = TRUE)
```

**CATEGORICALS PNG**
This plot shows how much urbanites spent on jewelry. The .png is located in the DV_RProject3 folder.
```{r}
source("../02 Data Wrangling/Categoricals.r", echo = TRUE)
```

